Improving Estimates of the State of Global Fisheries <br> Depends on Better Data

### 2021-06-18 documents/ovando-etal-assessing-global-fisheries.Rmd
version sent out for comments from authors

---
title: Improving Estimates of the State of Global Fisheries <br> Depends on Better Data
date: "`r Sys.Date()`"
bibliography: ["../references.bib"]
csl: fish-and-fisheries.csl
output: 
  bookdown::pdf_document2:
    latex_engine: xelatex
  bookdown::word_document2:
    reference_docx: template.docx
params:
  results_name: ["v1.0"]
  min_years_catch: [25]
always_allow_html: true
linkcolor: blue
header-includes:
  - \usepackage{setspace}\doublespacing
  - \usepackage{lineno}\linenumbers
toc: false
---

@@

The United Nations Sustainable Development Goal 14 (SDG 14), focusing on "Life under water", calls for the global community to "Conserve and sustainably use the oceans, seas and marine resources for sustainable development". Marine fisheries are one of the largest anthropogenic impacts in the oceans aside from the effects of climate change. When managed sustainably fisheries are a critical source of economic prosperity and food security around the globe. As such, meeting the SDG 14 targets depends in part on our ability to effectively measure the status of global marine fish populations and fisheries. While our understanding of the state of world fisheries has improved over the last decade, the majority of the world's fish populations, making up roughly 50% of marine landings, lack formal statistical assessments (stock assessments) of their population size relative to reference points [@hilborn2020; @fao2020]. This is a major impediment to ensuring the sustainable development of the world's oceans. In this paper, we consider why the assessment of global fisheries remains a challenge, and chart a path towards a better understanding of the state of the world's marine resources.

@@

The basis of this analysis is a new stock assessment software package we call [sraplus](https://github.com/DanOvando/sraplus) (https://github.com/DanOvando/sraplus). sraplus is an extension of stochastic stock reduction analysis (SRA) [@kimura1984;@walters2006], which allows users to combine a biomass dynamics model with a variety of data sources (e.g. priors on recent stock status, or an index of abundance) in order to produce estimates of the state of a fishery over time. The key goal of sraplus is not substantial improvements in model fitting methods per say, but providing the ability to easily incorporate multiple kinds of fishery data potentially used in SRA style analyses in a statistically rigorous manner. We paired various types of data with fisheries in RLSADB, and then used sraplus to generate predictions of *B/B~MSY~* in the most recent year of each fishery across different combinations of data types. We then compared the predictions generated by sraplus using different types of data, along with predictions for the same fisheries generated by CMSY, to the reported values in RLSADB.

@@

Where $B_t$ is biomass at time *t*, *K* is carrying capacity ,*r* is the intrinsic growth rate, *m* is the scaling parameter that allows for the ratio of *B~MSY~/K* to shift. When *m* = 2, *B~MSY~ / K* = 0.5. Lower values of *m* shift the production function left, higher values right. The shape parameter *m* is usually not reliably estimable given available data for surplus production models, however, @thorson2012 provides estimates of the ratio of *B~MSY~* to *K* for many fish taxa. For each stock we fix the shape parameter based on the distributions reported in @thorson2012 for the genus of the species in question. We chose to fix the shape parameter at the mean stock-appropriate values from @thorson2012 rather than estimating the shape parameter with an informative prior since there is so little information regarding the shape in the data considered. Attempts to estimate the shape parameter with priors from @thorson2012 frequently resulted in poor model performance. $\pmb{c}$ is a vector of catches, and $\pmb{p}$ is vector of process errors. Growth rates can become unrealistically large when the population reaches low sizes under the Pella-Tomlinson model. We deal with this problem by following the methods described in [@winker2018] to reduce the production of the population when it falls below a threshold of 25% of carrying capacity.

@@

All of our estimates are Bayesian in nature. sraplus can be run in two forms: either as a stock reduction analysis [SRA, @walters2006], or fit to an index of abundance (fishery dependent or independent) using Hamiltonian Monte Carlo with the No-U-Turn sampler [@hoffman2011]. Unless there is an abundance index to fit to, the model runs as an SRA. A stock reduction analysis works by specifying prior distributions on population parameters and, critically, the recent state of the fishery. sraplus allows users to specify the most recent status in units of depletion, *B/B~MSY~*, *F*, or *F/F~MSY~*. We then sample from the prior distributions of the population model parameters and apply those to the production model, along with the catch history. Any run that results in the collapse of the population (catch greater than biomass in any time step) is immediately rejected. The remaining viable draws from the prior distributions are sampled in proportion to the supplied prior on recent stock status. All stock reduction analysis runs in our paper sampled 2,000 draws of the prior-predictive distribution from a total of 1e^6^ candidate draws. For our main sets of results (everything excluding the value of information analysis), the estimated parameters are *r*, *K*, $\sigma_{proc}$, and *B/K~0~* (initial depletion). *q* is also estimated when needed. $\sigma_{proc}$ is estimated indirectly through the parameter $\gamma$, the ratio of process (*proc*) to observation (*obs*) error ($\sigma_{obs}$). See Table SX for prior distributions for each of these parameters.

@@

$$log(a_t) \sim N(f_{pt}(r,K,m,B0,\pmb{p},\pmb{c}) \times q, \sigma_{obs})$$

@@

$$log(cpue_t) \sim N(f_{pt}(r,K,m,B0,\pmb{p},\pmb{c}), \sigma_{obs})$$

@@

This may seem like an academic concern, and indeed in our experience when the data are sufficiently informative the Bayesian version of our model subject to Borel's paradox produces effectively identical results to those produce by the same model fit by maximum likelihood. Borel's Paradox poses a particular problem when there are no data to fit to though (i.e. when the model is simply filtering through prior distributions in the manner of a traditional SRA). Due to the fact that there are more ways for a fishery to be relatively unexploited than for a fishery to be close to collapse. In this context Borel's Paradox causes the posterior distribution of stock status to be positively biased relative to the supplied prior (although combined with other modeling choices can result in a net negative bias in stock status, @free2020). This process can also make it easy for users to accidentally supply very informative priors on stock status, without realizing that choices relating to population biology priors that may appear independent of stock status are in fact dictating the posterior distributions of stock status resulting from the SRA algorithm.

We use an approximate solution to this problem here, similar in spirit to Bayesian melding [@poole2000]. Our solution amounts to a two-step sampling-importance-resampling (SIR) algorithm. We first run the standard SIR algorithm as described in the Estimation Model section of the methods. We then break the resulting draws into bins based on terminal stock status, and calculate the mean probability density *p* (defined by the prior distributions of estimated parameters) of each bin.

@@

We then fit a range of models utilizing different combinations FMI, SAR, and effort data, along with CMSY, and a set of runs fit to the RLSADB Index (Table.\@ref(tab:dat-desc)). We assessed model performance using three metrics: median percent error (MPE, a measure of bias), median absolute percent error (MAPE, a measure of accuracy), and classification accuracy. Classification accuracy was calculated as the proportion of times that use of a given combination of data resulted in a stock being classified into the correct FAO status classification (one of underfished, maximally sustainably fished, and overfished). This experiment structure allows us to assess the ability of catch-only models to estimate the *B/B~MSY~* values reported in RLSADB, and evaluate how much these estimates can be improved by augmenting the catch histories with additional sources of information. Our benchmark model is a simple "Guess". Guess assigns each stock a random *B/B~MSY~* of 1.6, 1, or 0.4, corresponding to the middle value of the FAO status bins of underfished  ($B/B~MSY~ \geq 1.2$), maximally sustainably fished ($0.8 \geq B/B~MSY~ < 1.2$), overfished  ($0 \geq B/B~MSY~ < 0.8$). We performed a matching analysis measuring performance in estiamting *F/F~MSY~* as well, with results presented in the SI.

@@

We performed a value of information assessment to determine what types of data may be most beneficial to acquire at a global scale if we are to improve our knowledge of the state of global fisheries. The value of information analysis was performed by using sraplus to generate estimates of *B/B~MSY~* for stocks in RLSADB, and comparing the estimated values to the values reported in RLSADB. There are too many combinations for us to run the full expansion of possible parameter states. To resolve this we generated fits for 3000 combinations of a RLSADB stock and available data. For any one draw, we randomly sampled a RLSADB stock and a list of available data and data quality. For example, we might sample stock *A* with information on recent fishing mortality rates for the first iteration, and stock *A* again for the second iteration but now with information on recent fishing mortality rates and a recent index of abundance. The result is a set of model performance estimates where the characteristics of the stock and the data made available to the model are randomized. We then measured the value of information as the average reduction in root mean squared error (RMSE) in *B/B~MSY~* over the most recent five years of the fishery (in order to evaluate the ability of the model to capture recent trends as well as the most recent value), resulting from use of different kinds of data. We considered the value of information of having data on: the most recent *B/B~MSY~*, treating initial state of the population as one of unfished ($B/K_{0}=1$), known ($B/K_{0}$ taken from stock assessment), or estimated based on initial shape of the catch history, *F/F~MSY~* values in the most recent year, over the last five years, and over the complete time series, and an abundance index spanning the complete, most recent half, or most recent quarter of the time series. We considered the value of information of a longer time series of *F/F~MSY~* than *B/B~MSY~* to consider the potential of augmenting catch-only models with additional data that can inform *F/F~MSY~*, such as length-composition data, that might be available over the history of the fishery.

@@

Nearly all of the fisheries used in this case study have *F/F~MSY~* values less than one, and most have *B/B~MSY~* values greater than one. Both the catch heuristic implemented in sraplus and CMSY, using no stock-specific information but the catch history (which defines the prior on K and stock depletion, and hence the estimate of *B/B~MSY~*) and the estimated resilience of the target species (based on Fishlife [@thorson2020]), badly miss this trend, predicting instead that nearly all the fisheries in this group are currently overfished and experiencing overfishing. Adding priors informed by stock-specific swept area ratio and Fisheries Management Index data produces some improvements (RMSE below 1 relative to above 1 for all other case studies), capturing the general state that most of these fisheries have low fishing mortality rates and biomass near or above B~MSY~. Fitting to an index of abundance created by regional effort data in fact produces a slightly poorer fit in *B/B~MSY~* and *F/F~MSY~*. This is largely because a number of stocks in this case study set have very low catches (relative to historic highs) but high biomass values, creating a mismatch between the CPUE trends based on the effort and catch data and actual biomass. However none of the models fit to the four case-study data combinations were able to explain much of the variation in *B/B~MSY~*, though the models performed better in some cases for predicting *F/F~MSY~*. Models informed by the SAR and FMI values performed the best in terms of *B/B~MSY~* (RMSE = 0.89). The ranking of performance by data sources used was the same for *F/F~MSY~*, though the range of values was much higher, with the SAR and FMI based result producing an RMSE of 0.39 while the catch-only case studies produced *F/F~MSY~* RMSE values greater than 1 (Fig.\@ref(fig:cs-plot)). However, this improved performance of the SAR and FMI data is to be expected as the prior-generating models were trained on data from RLSADB, and therefore this is likely an optimistic assessment of the performance of these prior-generating models when applied to new fisheries.

@@

We first considered the performance of sraplus when the model was given a perfect index of abundance from RLSADB (RLSADB Index) for each stock in RLSADB it was tasked with assessing. Assessment models in RLSADB are typically much more structurally complex than the simple biomass dynamics used in sraplus, and so this "perfect information" test tells us how much of a penalty in model performance we are likely to pay due to model misspecification alone. The sraplus estimates of *B/B~MSY~* resulting from fitting directly to the abundance indices from RLSADB were relatively accurate and unbiased at a macro level (MPE `r percent(perf$mpe[perf$"Data Used" == "RLSADB Index"])`,MAPE `r percent(perf$mape[perf$"Data Used" == "RLSADB Index"])`, accuracy = `r percent(perf$accuracy[perf$"Data Used" == "RLSADB Index"])`, Table.\@ref(tab:perf-tab), Fig.\@ref(fig:mpe-map)-\@ref(fig:acc-map)). This exercise tells us that given sufficiently high quality data, a surplus production model such as sraplus is reasonably capable of reproducing the global state of fisheries as understood from formally assessed fisheries.

@@

Global-level assessments of fish populations are critical for guiding management agendas for the world's oceans, and tracking indicators such as the United Nations Sustainable Development Goals. The hope of efforts using catch-only models to estimate the status of global unassessed fisheries is fundamentally that we can learn something meaningful about the state of a fished population simply by knowing something about its catch history and life history. While in some cases the addition of globally available data such a FMI scores, SAR values, or effort reconstructions, provided value above and beyond catch histories alone (Fig.\@ref(fig:cs-plot)), at the global level models fit using each of the available datasets, besides the RLSADB-derived indices, generally produced biased and imprecise estimates of fish stock status (Table.\@ref(tab:perf-tab)).

@@

Our claim is that achieving substantial progress in assessing the state of global fisheries will require improved data and capacity building. This claim cannot be definitively proven; It is possible that some yet-to-be discovered model will provide a reliable means of dramatically improving the accuracy of estimates produced by models using current broadly-available datasets, such as catch-only style methods. Should that occur we will be happy to have been proven wrong. However, efforts from numerous groups made up of highly skilled scientists tasked with solving this problem have all come up short, particularly when external efforts tried validate their performance [@free2020;@bouch2021;@pons2020]. This is not intended as an indictment of those past efforts, but, we believe, a reflection on the limited amount of broadly applicable predictive power that exists within catch histories alone. Methods tested in those papers have been demonstrated to perform relatively well when given data or priors informative to specific fisheries. We revisited this task in this paper, and found that even when augmented with other broadly available datasets, we were unable to produce consistently accurate estimates of stock status around the globe. For these reasons we believe that improvements to our understanding of the state of global unassessed fisheries will come from targeted use of existing data, and expanding the collection of high-priority data around the globe, rather than the development of new modeling methods alone.

We chose to test the performance of methods against estimated values reported in RLSADB. A reasonable critique of this choice is that unassessed stocks, on which these methods would actually be used, are likely to have vastly different dynamics than the heavily managed fish populations represented in RLSADB, in addition to the errors in the RLSADB estimates themselves. For this reality to change our results though would require that the methods tested here have massively lower bias and higher accuracy for unassessed fisheries than RLSADB stocks. @free2020's simulation based results of these same types of models suggests that this is unlikely to be true. However, while many assessed fisheries have mechanisms to actively manage catches, catch histories in unassessed and unmanaged fisheries may be more likely to reflect underlying stock status than those in heavily regulated fisheries.

@@

Our results do not imply that the kinds of broadly available data presented here are not valuable under the right conditions. The FMI and SAR based priors are an improvement over catch-only models in applicable situations (i.e. those that sufficiently resemble the data on which the regressions were trained, Fig.\@ref(fig:cs-plot)). Effort data such as those reconstructed by @rousseau2019 can help distinguish between regions with similar catch histories but different large-scale effort trajectories, and may be quite useful as indices of abundance for areas with good knowledge of rates of evolution of fishing technology and a broadly selective fishing fleet. Despite not adding a great deal in terms of performance at the global scale, swept-area-ratio was the strongest predictor of *F/F~MSY~* of any of the datasets we explore on an individual stock basis, with a Bayesian R^2^ value of `r round(mean(rstanarm::bayes_R2(sraplus::sar_models$fit[[3]])),2)`. But, we must simultaneously consider data quality and resolution: applying one SAR value to all stocks in a region, even if that SAR value can provide valuable information for a subset of fisheries, causes inaccurate estimates of stock status when applied too broadly. Our analysis does not show that the data considered here are without value, but that attempting to indiscriminately apply these data to all areas of the globe results in meaningfully incorrect estimates of stock status for regions whose nature does not match the assumptions needed to apply these data sources. We found that performance of different data sources varied widely both within and among regions (Fig.\@ref(fig:cs-plot), Fig.\@ref(fig:mpe-map)-\@ref(fig:acc-map)). Some of this variation is likely simply due to low sample sizes of assessed stocks reported in the RLSADB in some regions. But, other explanations for differences in performance among stocks and regions may be an interesting area for future research. For example, it may be that stocks in some regions are more suitable to being represented by surplus production models than others.

@@

We must also prioritize collection and curation of fish population survey data worldwide. Repositories of fishery-independent survey data would be immensely beneficial, such as those maintained by [FishStat](https://www.FishStats.org) ( www.FishStats.org). Recent research confirms that there are bottom trawl data to support analysis of biomass-trends since 2001 and potentially earlier in many regions [@maureaud2020], and survey data are available for more stocks than have stock assessments. Effort reconstructions such as those utilized here may help create fishery-dependent abundance indices in some instances, and going forward datasets such as those compiled by [Global Fishing Watch](https://globalfishingwatch.org/)(https://globalfishingwatch.org/) in combination with the reconstruction approaches of @rousseau2019 might allow us to construct and use timeseries of fishing effort specific to particular areas, fleets, and species complexes. However, our value of information exercise indicates that we may have to wait many years for new surveys to provide substantial improvements in status estimates (Fig.\@ref(fig:voi-plot)).

>>>>

---
title: Improving Estimates of the State of Global Fisheries <br> Depends on Better Data
date: "`r Sys.Date()`"
bibliography: ["../references.bib"]
csl: fish-and-fisheries.csl
output: 
  bookdown::word_document2:
    reference_docx: template.docx
  bookdown::pdf_document2:
    latex_engine: xelatex
params:
  results_name: ["v1.0"]
  min_years_catch: [25]
always_allow_html: true
linkcolor: blue
header-includes:
  - \usepackage{setspace}\doublespacing
  - \usepackage{lineno}\linenumbers
toc: false
---

@@

The United Nations Sustainable Development Goal 14 (SDG 14), focusing on "Life under water", calls for the global community to "Conserve and sustainably use the oceans, seas and marine resources for sustainable development". Marine fisheries are one of the largest anthropogenic impacts in the oceans aside from the effects of climate change. Fisheries are also a critical source of economic prosperity, cultural identity, and food security around the globe. As such, meeting the SDG 14 targets depends in part on our ability to effectively measure the status of global marine fish populations and fisheries. While our understanding of the state of world fisheries has improved over the last decade, the majority of the world's fish populations, making up roughly 50% of marine landings (though only a few percent of the total number of fisheries in the world), lack formal statistical assessments (stock assessments) of their population size relative to reference points [@hilborn2020; @fao2020]. This is a major impediment to ensuring the sustainable development of the world's oceans. In this paper, we consider why the assessment of global fisheries remains a challenge, and chart a path towards a better understanding of the state of the world's marine resources.

@@

The basis of this analysis is a new stock assessment software package we call [sraplus](https://github.com/DanOvando/sraplus) (https://github.com/DanOvando/sraplus). sraplus is an extension of stochastic stock reduction analysis (SRA) [@kimura1984;@walters2006], which allows users to combine a biomass dynamics model with a variety of data sources (e.g. priors on recent stock status, or an index of abundance) in order to produce estimates of the state of a fishery over time. The key goal of sraplus is not substantial improvements in model fitting methods per say, but providing the ability to easily incorporate multiple kinds of fishery data potentially used in SRA-style analyses in a statistically rigorous manner. We paired various types of data with fisheries in RLSADB, and then used sraplus to generate predictions of *B/B~MSY~* in the most recent year of each fishery across different combinations of data types. We then compared the predictions generated by sraplus using different types of data, along with predictions for the same fisheries generated by CMSY, to the reported values in RLSADB.

@@

Where $B_t$ is biomass at time *t*, *K* is carrying capacity ,*r* is the intrinsic growth rate, *m* is the scaling parameter that allows for the ratio of *B~MSY~/K* to shift. When *m* = 2, *B~MSY~ / K* = 0.5. Lower values of *m* shift the production function left, higher values right. The shape parameter *m* is usually not reliably estimable given available data for surplus production models, however, @thorson2012 provides estimates of the ratio of *B~MSY~* to *K* for many fish taxa. For each stock we fix the shape parameter based on the distributions reported in @thorson2012 for the genus of the species in question. We chose to fix the shape parameter at the mean stock-appropriate values from @thorson2012 rather than estimating the shape parameter with an informative prior since there is so little information regarding the shape in the data considered. Attempts to estimate the shape parameter with priors from @thorson2012 frequently resulted in poor model performance. $\pmb{c}$ is a vector of catches, and $\pmb{p}$ is vector of process errors. Growth rates can become unrealistically large when the population reaches low sizes under the Pella-Tomlinson model. We dealt with this problem by following the methods described in @winker2018 to reduce the production of the population when it falls below a threshold of 25% of carrying capacity.

@@

All of our estimates are Bayesian in nature. sraplus can be run in two forms: either as a stock reduction analysis [SRA, @walters2006], or fit to an index of abundance (fishery dependent or independent) using Hamiltonian Monte Carlo with the No-U-Turn sampler [@hoffman2011]. Unless there is an abundance index to fit to, the model runs as an SRA. A stock reduction analysis works by specifying prior distributions on population parameters and, critically, the recent state of the fishery. sraplus allows users to specify the most recent status in units of depletion, *B/B~MSY~*, *F*, or *F/F~MSY~*. We then sample from the prior distributions of the population model parameters and apply those to the production model, along with the catch history. Any run that results in the collapse of the population (catch greater than biomass in any time step) is immediately rejected. The remaining viable draws from the prior distributions are sampled in proportion to the supplied prior on recent stock status. All stock reduction analysis runs in our paper sampled 2,000 draws of the prior-predictive distribution from a total of 1e^6^ candidate draws. For our main sets of results (everything excluding the value of information analysis), the estimated parameters are *r* (with a prior distribution drawn from Fishlife, @thorson2020), *K*, $\sigma_{proc}$, and *B~0~* (initial depletion, $B/K$). *q* is also estimated when needed. $\sigma_{proc}$ (process error) is estimated indirectly through the parameter $\gamma$, the ratio of process (*proc*) to observation (*obs*) error ($\sigma_{obs}$). See Table.S1 for prior distributions for each of these parameters.

@@

$$log(a_t) \sim N(f_{pt}(r,K,m,B_0,\pmb{p},\pmb{c}) \times q, \sigma_{obs})$$

@@

$$log(cpue_t) \sim N(f_{pt}(r,K,m,B_0,\pmb{p},\pmb{c}), \sigma_{obs})$$

@@

This may seem like an academic concern, and indeed in our experience when the data are sufficiently informative the Bayesian version of our model subject to Borel's paradox produces effectively identical results to those produce by the same model fit by maximum likelihood. However, Borel's Paradox poses a particular problem when there are no data to fit to(i.e. when the model is simply filtering through prior distributions in the manner of a traditional SRA) due to the fact that there are more parameter combinations that allow for a fishery to be relatively unexploited than for a fishery to be close to collapse (but never actually collapsed, i.e. predicted biomass less than observed catch). In this context Borel's Paradox causes the posterior distribution of stock status to be positively biased relative to the supplied prior (although combined with other modeling choices can result in a net negative bias in stock status, @free2020). This process can also make it easy for users to accidentally supply very informative priors on stock status, without realizing that choices relating to population biology priors that may appear independent of stock status are in fact dictating the posterior distributions of stock status resulting from the SRA algorithm.

We use an approximate solution to this problem here, similar in spirit to Bayesian melding [@poole2000]. Our solution amounts to a two-step sampling-importance-resampling (SIR) algorithm. We first run the standard SRA algorithm as described in the Estimation Model section of the methods. We then break the resulting draws into bins based on terminal stock status, and calculate the mean probability density *p* (defined by the prior distributions of estimated parameters) of each bin.

@@

We then fit a range of models utilizing different combinations FMI, SAR, and effort data, along with CMSY, and a set of runs fit to the RLSADB Index (Table.\@ref(tab:dat-desc)). We assessed model performance using three metrics: median percent error (MPE, a measure of bias), median absolute percent error (MAPE, a measure of accuracy), and classification accuracy. Classification accuracy was calculated as the proportion of times that use of a given combination of data resulted in a stock being classified into the correct FAO status classification (one of underfished, maximally sustainably fished, and overfished). This experiment structure allows us to assess the ability of catch-only models to estimate the *B/B~MSY~* values reported in RLSADB, and evaluate how much these estimates can be improved by augmenting the catch histories with additional sources of information. Our benchmark model is a simple "Guess". Guess assigns each stock a random *B/B~MSY~* of 1.6, 1, or 0.4, corresponding to the middle value of the FAO status bins of underfished  ($B/B~MSY~ \geq 1.2$), maximally sustainably fished ($0.8 \geq B/B~MSY~ < 1.2$), overfished  ($0 \geq B/B~MSY~ < 0.8$). We performed a matching analysis measuring performance in estimating *F/F~MSY~* as well, with results presented in the SI.

@@

We performed a value of information assessment to determine what types of data may be most beneficial to acquire at a global scale if we are to improve our knowledge of the state of global fisheries. The value of information analysis was performed by using sraplus to generate estimates of *B/B~MSY~* for stocks in RLSADB, and comparing the estimated values to the values reported in RLSADB. There are too many combinations for us to run the full expansion of possible parameter states. To resolve this we generated fits for 3000 combinations of a RLSADB stock and available data. For any one draw, we randomly sampled a RLSADB stock and a list of available data and data quality. For example, we might sample stock *A* with information on recent fishing mortality rates for the first iteration, and stock *A* again for the second iteration but now with information on recent fishing mortality rates and a recent index of abundance. The result is a set of model performance estimates where the characteristics of the stock and the data made available to the model are randomized. We then measured the value of information as the average reduction in root mean squared error (RMSE) in *B/B~MSY~* over the most recent five years of the fishery (in order to evaluate the ability of the model to capture recent trends as well as the most recent value), resulting from use of different kinds of data. We considered the value of information of having data on: the most recent *B/B~MSY~*, treating initial state of the population as one of unfished ($B_{0}=1$), known ($B_{0}$ taken from stock assessment), or estimated based on initial shape of the catch history, *F/F~MSY~* values in the most recent year, over the last five years, and over the complete time series, and an abundance index spanning the complete, most recent half, or most recent quarter of the time series. We considered the value of information of a longer time series of *F/F~MSY~* than *B/B~MSY~* to consider the potential of augmenting catch-only models with additional data that can inform *F/F~MSY~*, such as length-composition data, that might be available over the history of the fishery.

@@

Nearly all of the fisheries used in this case study have *F/F~MSY~* values less than one, and most have *B/B~MSY~* values greater than one. Both the catch heuristic implemented in sraplus and CMSY, using no stock-specific information but the catch history (which defines the prior on K and stock depletion, and hence the estimate of *B/B~MSY~*) and the estimated resilience of the target species used to provide a prior on *r* (based on Fishlife, @thorson2020), badly miss this trend, predicting instead that nearly all the fisheries in this group are currently overfished and experiencing overfishing (Fig.\@ref(fig:cs-plot)). Overall, models informed by the SAR and FMI values performed the best in terms of *B/B~MSY~* (RMSE = 0.89). The ranking of performance by data sources used was the same for *F/F~MSY~*, though the range of values was much higher, with the SAR and FMI based result producing an RMSE of 0.39 while the catch-only case studies produced *F/F~MSY~* RMSE values greater than 1 (Fig.\@ref(fig:cs-plot)). However, this improved performance of the SAR and FMI data is to be expected as the prior-generating models were trained on data from RLSADB, and therefore this is likely an optimistic assessment of the performance of these prior-generating models when applied to new fisheries.  Fitting to an index of abundance created by regional effort data in fact produces a slightly poorer fit in *B/B~MSY~* and *F/F~MSY~*. This is likely because a number of stocks in this case study set have very low catches (relative to historic highs) but high biomass values, creating a mismatch between the CPUE trends based on the effort and catch data and actual biomass. However none of the models fit to the four case-study data combinations were able to explain much of the variation in *B/B~MSY~*, though the models performed better in some cases for predicting *F/F~MSY~*.

@@

We first considered the performance of sraplus when the model was given a perfect index of abundance from RLSADB (RLSADB Index) for each stock in RLSADB it was tasked with assessing. Assessment models in RLSADB are typically much more structurally complex than the simple biomass dynamics used in sraplus, and so this "perfect information" test tells us how much of a penalty in model performance we are likely to pay due to model misspecification alone. The sraplus estimates of *B/B~MSY~* resulting from fitting directly to the abundance indices from RLSADB were relatively accurate and unbiased at a macro level (MPE `r percent(perf$mpe[perf$"Data Used" == "RLSADB Index"])`,MAPE `r percent(perf$mape[perf$"Data Used" == "RLSADB Index"])`, accuracy = `r percent(perf$accuracy[perf$"Data Used" == "RLSADB Index"])`, Table.\@ref(tab:perf-tab), Fig.\@ref(fig:mpe-map)-\@ref(fig:acc-map)). This exercise tells us that given sufficiently high quality index of abundance, a surplus production model such as sraplus is reasonably capable of reproducing the global state of fisheries as understood from formally assessed fisheries.

@@

Global-level assessments of fish populations are critical for guiding management agendas for the world's oceans, and tracking indicators such as the United Nations Sustainable Development Goals. The hope of efforts using catch-only models to estimate the status of global unassessed fisheries is fundamentally that we can learn something meaningful about the state of a fished population simply by knowing something about its catch history and life history. While in some cases the addition of globally available data such a FMI scores, SAR values, or effort reconstructions, provided value above and beyond catch histories alone (Fig.\@ref(fig:cs-plot)), at the global level models fit using each of the available datasets, besides the RLSADB-derived indices, generally produced biased and imprecise estimates of fish stock status (Table.\@ref(tab:perf-tab)). The simplicity and low data requirements of catch-only models are understandably appealing to many users, but our results highlight that without high-quality local data these methods can provide highly imprecise and biased results. Broad and uncritical application of these methods that frequently result in incorrect classification of stock status can be detrimental to both ecosystems and livelihoods.

Our claim is that achieving substantial progress in assessing the state of global fisheries will require improved data and capacity building. This claim cannot be definitively proven; it is possible that some yet-to-be discovered model will provide a reliable means of dramatically improving the accuracy of estimates produced by catch-based models using current broadly-available datasets. Basic logic tells us though that such a model would have to depend on strong assumptions, new data, or empirical estimation. Catch is a function of catchability, effort, and biomass, so given just catch we have one equation and three unknowns. Structurally separating out biomass (and subsequently estimating reference points etc.) requires then either data or strong assumptions on these other variables across a sufficiently representative timespan. Alternatively, empirical relationships could be developed linking attributes of catch histories to observed estimates of stock status [e.g. @costello2012b]. However, these methods require that these empirical relationships both exist and are reliably preserved in fisheries that lack formal assessments. Numerous groups made up of highly skilled scientists have attempted to resolve these fundamental challenges in various ways, but external efforts to validate the performance of these methods have consistently found them to perform generally poorly when applied in bulk [@free2020;@bouch2021;@pons2020]. This is not intended as an indictment of those past efforts, but, we believe, a reflection on the limited amount of broadly applicable predictive power that exists within catch histories alone. Methods tested in those papers have been demonstrated to perform relatively well when given specific data or priors informative to specific fisheries. We revisited this task in this paper, and found that even when augmented with other broadly available datasets, we were unable to produce consistently accurate estimates of stock status around the globe. For these reasons we believe that improvements to our understanding of the state of global unassessed fisheries will come from targeted use of existing but underutilized data, and expanding the collection of high-priority data around the globe, rather than the development of new modeling methods alone.

@@

Our fits to the RLSADB data provide a useful diagnostic of the degree to which model mispecification might explain the poor performance of catch-only models. Catch-only models generally employ some form of biomass dynamics model, such as the Schaefer surplus production model [@schaefer1954]. These models are generally much simpler than the typically age-structured population models underpinning the assessments in the RLSADB. While we found that fitting the Pella-Tomlinson model employed in sraplus to an index of abundance drawn directly from the RLSADB provided much improved and reasonably accurate estimates of stock status relative to catch-only approaches (Table.\@ref(tab:perf-tab)), even with the index of abundance sraplus still had an average MAPE of `r scales::percent(perf$mape[perf$'Data Used' == "RLSADB Index"])`. This discrepancy may provide a measure of relatively insurmountable error resulting from model misspecification that inclusion of additional data may not be able to overcome.  For example, many assessments in the RLSADB calculate *B/B~MSY~* based on spawning stock biomass. However, surplus production models condition the size and state of the population on the catch, which is by definition a measure of the vulnerable biomass. Vulnerable biomass may not reliably track spawning biomass in highly selective fisheries, potentially resulting in model biases as the surplus production model is not capable of separately tracking spawning and vulnerable biomass.

We chose to test the performance of methods against estimated values reported in RLSADB. A reasonable critique of this choice is that unassessed stocks, on which these methods would actually be used, are likely to have vastly different dynamics than the heavily managed fish populations represented in RLSADB, in addition to the errors in the RLSADB estimates themselves. For this reality to change our results though would require that the methods tested here have massively lower bias and higher accuracy for unassessed fisheries than RLSADB stocks. @free2020's simulation based results of these same types of models suggests that this is unlikely to be true. However, while many assessed fisheries have mechanisms to actively manage catches, catch histories in unassessed and unmanaged fisheries may be more likely to reflect underlying stock status than those in relatively well managed fisheries, though any predictive relationship will still depend on a host of factors such as changes in effort. This could be empirically tested by considering the performance of catch-only models on data from earlier in the history of fisheries in the RLSADB, though we did not do so here as we do not have historic estimates of FMI or SAR values.

@@

Our results do not imply that the kinds of broadly available data presented here are not valuable under the right conditions. The FMI and SAR based priors are an improvement over catch-only models in applicable situations (i.e. those that sufficiently resemble the data on which the regressions were trained, Fig.\@ref(fig:cs-plot)). Effort data such as those reconstructed by @rousseau2019 can help distinguish between regions with similar catch histories but different large-scale effort trajectories, and may be quite useful as indices of abundance for areas with good knowledge of rates of evolution of fishing technology and a broadly selective fishing fleet. Despite not adding a great deal in terms of performance at the global scale, swept-area-ratio was the strongest predictor of *F/F~MSY~* of any of the datasets we explore on an individual stock basis, with a Bayesian R^2^ value of `r round(mean(rstanarm::bayes_R2(sraplus::sar_models$fit[[3]])),2)` (see SI). But, we must simultaneously consider data quality and resolution: applying one SAR value to all stocks in a region, even if that SAR value can provide valuable information for a subset of fisheries, causes inaccurate estimates of stock status when applied too broadly. Our analysis does not show that the data considered here are without value, but that attempting to indiscriminately apply these data to all areas of the globe results in meaningfully incorrect estimates of stock status for regions whose nature does not match the assumptions needed to apply these data sources. We found that performance of different data sources varied widely both within and among regions (Fig.\@ref(fig:cs-plot), Fig.\@ref(fig:mpe-map)-\@ref(fig:acc-map)). Some of this variation is likely simply due to low sample sizes of assessed stocks reported in the RLSADB in some regions. But, other explanations for differences in performance among stocks and regions may be an interesting area for future research. For example, it may be that stocks in some regions are more suitable to being represented by surplus production models than others.

@@

We must also prioritize collection and curation of fish population survey data worldwide. Repositories of fishery-independent survey data would be immensely beneficial, such as those maintained by [FishStat](https://www.FishStats.org) ( www.FishStats.org). Recent research confirms that there are bottom trawl data to support analysis of biomass-trends since 2001 and potentially earlier in many regions [@maureaud2020], and survey data are available for more stocks than have stock assessments. Effort reconstructions such as those utilized here may help create fishery-dependent abundance indices in some instances, and going forward datasets such as those compiled by [Global Fishing Watch](https://globalfishingwatch.org/) (https://globalfishingwatch.org/) in combination with the reconstruction approaches of @rousseau2019 might allow us to construct and use timeseries of fishing effort specific to particular areas, fleets, and species complexes. However, our value of information exercise indicates that we may have to wait many years for new surveys to provide substantial improvements in status estimates (Fig.\@ref(fig:voi-plot)).

Expanded training of fisheries scientists around the globe is another critical need. Even were we to dramatically expand the amount and types of data available for global assessment, individual fisheries and regions will need to make informed decisions about which sources of data may be applicable and which not, and to critically evaluate the results of any model based on local expertise. This is why stock assessments even in data-rich fisheries are not an automated process; the real challenge is often not in fitting a model to data but in understanding how best to use the data and the quality and limitations of the model used. Empowering a global network of fisheries scientists through training and peer-support would help local experts make the most of available data, ensure the reliability of newly collected data, and improve the interpretation of assessment results. We may also need to acknowledge that in some fisheries reliable estimates of stock status relative to MSY based reference points are simply not possible (or perhaps desirable), and instead rely on more precautionary or empirical management management measures such as spatial closures, size restrictions, and indicator based harvest strategies (ideally tested through management strategy evaluation) [@prince2019;@dowling2015;@fulton2016].
